---
title: "CanonicalCorrelation"
author: "S18809"
date: "2024-05-26"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Loading Suitable Package
```{r}
library(ggplot2)
library(GGally)
library(CCA)#facilitates canonical correlation analysis
library(CCP)#facilitates checking the significance of the canonical variates
```
```{r}
library(dplyr)
```
```{r}
library(tidyverse)
```
```{r}
library(corrplot)
```


#### Loading the File
```{r}
bodyFat <- read_csv(file = "../Data/bodyfat.csv")
```
```{r}
colnames(bodyFat)
```

####  Check the null values for all columns
```{r}
colSums(is.na(bodyFat))
```
#### Dimension of the data
```{r}
dim(bodyFat)
```

#### Summary of the Data set
```{r}
summary(bodyFat)
```
## Canonical Correlation Analysis

```{r}
body_composition_metrics <- bodyFat[, 1:5] #U_ Xvariables
body_measurements <- bodyFat[, 6:15] #V_ Y variables
```

## Correlation matrix between each variables
```{r}
# Compute correlation matrix
correlation_matrix <- cor(bodyFat)

# Draw correlation matrix with customization
corrplot(correlation_matrix, method = "number", col = colorRampPalette(c("blue", "white", "red"))(10),
          type = "upper", order = "hclust", tl.col = "black", tl.srt = 45,
          addrect = 3, rect.col = "grey", number.cex = 0.7, tl.cex = 0.8,
          title = "Correlation Matrix")
```


```{r}
ggpairs(body_composition_metrics)
```

```{r}
ggpairs(body_measurements)
```


```{r}
#checking the between and within set associations
matcor(body_composition_metrics,body_measurements)
```


```{r}
#obtaining the canonical correlations
CC_bodyFat <- cc(body_composition_metrics,body_measurements)
```

### Display the Canonical Correlation
```{r}
CC_bodyFat$cor
```

```{r}
squared_canonical_correlations <- (CC_bodyFat$cor)^2
print("Squared Canonical Correlations:")
print(squared_canonical_correlations)
```


```{r}
#raw canonical coefficients
CC_bodyFat[3:4]
```


```{r}
# compute canonical loading
cc_bodyFat_2 <- comput(body_composition_metrics,body_measurements,CC_bodyFat)
```

```{r}
#displays the canonical loading
cc_bodyFat_2[3:6]
```
# Test the Canonical correlation
```{r}
rho <- CC_bodyFat$cor
```

## Define number of observations, number of variables in first set, and number of variables in the second set.
```{r}
n <- dim(body_composition_metrics)[1]
p <- length(body_composition_metrics)
q <- length(body_measurements)
```


## Calculate p-values using the F-approximations of different test statistics:
```{r}
p.asym(rho, n, p, q, tstat = "Wilks")
```
```{r}
p.asym(rho, n, p, q, tstat = "Hotelling")
```

```{r}
p.asym(rho, n, p, q, tstat = "Pillai")
```
```{r}
p.asym(rho, n, p, q, tstat = "Roy")
```

## Standardize the data set
```{r}
# Standardize first canonical variables
std_1<-diag(sqrt(diag(cov(body_composition_metrics))))
ss_1<- std_1%*%CC_bodyFat$xcoef
`rownames<-`(ss_1,c("Density","BodyFat","Age","Weight","Height"))
```
```{r}
# Standardize second canonical variables
std_2<-diag(sqrt(diag(cov(body_measurements))))
ss_2<- std_2%*%CC_bodyFat$ycoef
`rownames<-`(ss_2,c("Neck","Chest","Abdomen","Hip","Thigh","Knee","Ankle","Biceps"
                    ,"Forearm","Wrist"))
```






















